Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-26 paper/structureScene.tex
write more on the problem of converting to mono

\subsection{Binaural data augmentation}
The recording condition of most acoustic scene datasets follow a binaural protocol, \ie a pair of microphones respectively located over the ears of the recordist.
This protocol provides a realistic description of the spatial auditory environment, as it reproduces the natural listening conditions of humans.
% In particular, the inter-intensity difference (IID) between left and right channel conveys the approximate azimuth of each sound source that make up the scene with respect to the listener.
Yet, since the location of the recordist may vary across instances of the same class, the feature space for classification should be invariant to the location of sources.
In order to achieve invariance to location, averaging the left and right channels into a monophonic signal is by far the most widespread technique.

\begin{equation}
\boldsymbol{x}(t) =
\alpha \boldsymbol{\times x_\mathsf{L}}\!(t) +
(1-\alpha) \boldsymbol{\times x_\mathsf{R}}\!(t)
\end{equation}
In practice, $\alpha$ takes values in ${0\%, 25\%, 50\%, 75\%, 100\%}$.

>>>>

\subsection{Binaural data augmentation}
The recording condition of most acoustic scene datasets follow a binaural protocol, \ie a pair of microphones respectively located over the ears of the recordist.
This protocol provides a realistic description of the spatial auditory environment, as it reproduces the natural listening conditions of humans.
In particular, the interaural level difference (ILD) between left and right channel conveys the approximate azimuth of each sound source that make up the scene with respect to the listener. \vl{ref needed}
Yet, since the location of the recordist varies across instances of the same class, the feature space for classification should be invariant to these azimuths.

In order to achieve invariance to ILD, averaging the left and right channels into a monophonic signal is by far the most widespread approach.
An important drawback is that it biases the measurement towards the center of the scene, as lateral sources get damped.
%Moreover, sources 
\begin{equation}
\boldsymbol{x}(t) =
\alpha \boldsymbol{\times x_\mathsf{L}}\!(t) +
(1-\alpha) \boldsymbol{\times x_\mathsf{R}}\!(t)
\end{equation}
In practice, $\alpha$ takes values in ${0\%, 25\%, 50\%, 75\%, 100\%}$.
